A Meta-analysis of Longevity Estimates of Mosquito Vectors of Disease: Supplementary Material

### 2018-11-23 supplementary_materials.tex
Read up to `Statistical analysis of dissection data'

\begin{figure}[ht]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/dissection_parity_data3.png}}
	\caption{\textbf{The normalised physiological age series for nine species in the database.} Each different coloured line represents an individual series. In each case the count for all ages has been normalised by the nulliparous count. In all cases we do not include any data for censored observations (see Section \ref{sec:dissection_censored}).}\label{fig:dissection_exampleData3}
\end{figure}

@@

As for the MRR analysis we use \textit{Stan} that implements a form of MCMC algorithm known as NUTS \citep{hoffman2014no} to sample from the posterior. The protocol followed for the MCMC sampling was the same as described in Section \ref{sec:mrr_MCMC}.

>>>>

\begin{figure}[ht]
	\centerline{\includegraphics[width=1.3\textwidth]{./Figure_files/dissection_parity_data3.png}}
	\caption{\textbf{The normalised physiological age series for seven species in the database.} Each different coloured line represents an individual series. In each case the count for all ages has been normalised by the nulliparous count. In all cases we do not include any data for censored observations (see Section \ref{sec:dissection_censored}).}\label{fig:dissection_exampleData3}
\end{figure}

@@
